---
title: "Cheatsheet for the exam"
author: "Stephan.Huber@hs-fresenius.de"
date: "2024-01-12"

abstract: |
  In this report, I summarize operators and popular functions of R. Moreover, I present the output of all exercises. That should help you to answer exam questions.
  
format:
  html:
    embed-resources: true
    self-contained-math: true
---

# Packages to load for the exam

```{r echo=TRUE, message=FALSE}
if (!require(pacman)) install.packages("pacman")
pacman::p_load(jtools, janitor, haven, lubridate, forcats, stringr, dplyr, purrr, 
               readr, tidyr, tibble, ggplot2, tidyverse, kableExtra, pacman)

```

```{r include=FALSE}
pacman::p_unload(all)
```


# Links to solutions

1.  [exe_duplicates.R](https://raw.githubusercontent.com/hubchev/courses/main/scr/exe_duplicates.R)
2.  [exe_import_covid.R](https://raw.githubusercontent.com/hubchev/courses/main/scr/exe_import_covid.R)
2.  [exe_genanddrop.R](https://raw.githubusercontent.com/hubchev/courses/main/scr/exe_genanddrop.R)
3.  [exe_base_pipe.R](https://raw.githubusercontent.com/hubchev/courses/main/scr/exe_base_pipe.R)
4.  [exe_subset.R](https://raw.githubusercontent.com/hubchev/courses/main/scr/exe_subset.R)
5.  [data_transformation.R](https://raw.githubusercontent.com/hubchev/courses/main/scr/data_transformation.R)
6.  [exe_poser.R](https://raw.githubusercontent.com/hubchev/courses/main/scr/exe_poser.R)
7.  [datasaurus_solution.html](https://raw.githubusercontent.com/hubchev/courses/main/scr/datasauRus.R)
8.  [convergence.R](https://raw.githubusercontent.com/hubchev/courses/main/scr/convergence.R)
9.  [un_gdp_ger_fra.R](https://raw.githubusercontent.com/hubchev/courses/main/scr/un_gdp_ger_fra.R)
10. [hortacsu_figure_3.R](https://raw.githubusercontent.com/hubchev/courses/main/scr/hortacsu_figure_3.R) 
10. [regress_lecture.R](https://raw.githubusercontent.com/hubchev/courses/main/scr/regress_lecture.R)
11. [exe_calories.R](https://raw.githubusercontent.com/hubchev/courses/main/scr/exe_calories.R)
12. [bundesliga.R](https://raw.githubusercontent.com/hubchev/courses/main/scr/exe_bundesliga.R)
13. [exe_okun_solution.R](https://raw.githubusercontent.com/hubchev/courses/main/scr/exe_okun_solution.R)


# Script: exe_duplicates.R
```{r, file =   "https://raw.githubusercontent.com/hubchev/courses/main/scr/exe_duplicates.R"}
```

# Script: exe_import_covid.R
```{r, file = "https://raw.githubusercontent.com/hubchev/courses/main/scr/exe_import_covid.R"}
```


# Script: exe_genanddrop.R

```{r, file = "https://raw.githubusercontent.com/hubchev/courses/main/scr/exe_genanddrop.R"}
```

# Script: exe_base_pipe.R

```{r, file = "https://raw.githubusercontent.com/hubchev/courses/main/scr/exe_base_pipe.R"}
```

# Script: exe_subset.R

```{r, file =   "https://raw.githubusercontent.com/hubchev/courses/main/scr/exe_subset.R"}
```

# Script: exe_poser.R

```{r, file =   "https://raw.githubusercontent.com/hubchev/courses/main/scr/exe_poser.R"}
```

# Script: datasauRus.R

```{r, file =   "https://raw.githubusercontent.com/hubchev/courses/main/scr/exe_datasauRus.R"}
```

# Script: convergence.R

```{r, file =   "https://raw.githubusercontent.com/hubchev/courses/main/scr/exe_convergence.R"}
```

# Script: un_gdp_ger_fra.R

```{r, file =   "https://raw.githubusercontent.com/hubchev/courses/main/scr/exe_un_gdp_ger_fra.R"}
```

# Script: hortacsu_figure_3.R

```{r, file =   "https://raw.githubusercontent.com/hubchev/courses/main/scr/hortacsu_figure_3.R"}
```

# Script: regress_lecture.R

```{r, file =   "https://raw.githubusercontent.com/hubchev/courses/main/scr/regress_lecture.R"}
```

# Script: exe_calories.R

```{r, file =   "https://raw.githubusercontent.com/hubchev/courses/main/scr/exe_calories.R"}
```

# Script: bundesliga.R

```{r, file =   "https://raw.githubusercontent.com/hubchev/courses/main/scr/exe_bundesliga.R"}
```

# Script: exe_okun_solution.R

```{r, file =   "https://raw.githubusercontent.com/hubchev/courses/main/scr/exe_okun_solution.R"}
```

# Script: exe_zipf_solution.R

```{r, file =   "https://raw.githubusercontent.com/hubchev/courses/main/scr/exe_zipf_solution.R"}
```




```{r, echo=FALSE, eval=TRUE}
# Define source and destination paths
source_files <- c("exam_functions.qmd", "exam_functions.html")
destination_folder <- "/home/sthu/Dropbox/hsf/github/courses/rmd/"

# Copy files to the destination folder
file.copy(source_files, destination_folder, overwrite = TRUE)

# Print a message indicating the successful copy
cat("Files copied to", destination_folder, "\n")

```